%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% Website: https://github.com/sb2nov/resume
% License : MIT
%------------------------
\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}
\usepackage{hyperref}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\setlength{\footskip}{4.09pt}   % don't understand

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeItemNornal}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}
  \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheadingNoTitle}[2]{
  \vspace{-1pt}
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      %\textbf{#1} & #2 \\
      \textit{\small#1} & \textit{\small#2}
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}
\newcommand{\resumeSubItemNormal}[1]{\resumeItemNornal{#1}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{{\Large Nguyen Ngoc Thanh Tuyen}} & \\
  Data Engineer & \href{https://github.com/tuyen-nnt/myResume}{https://github.com/tuyen-nnt/myResume}
\end{tabular*}
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
    & \href{https://github.com/tuyen-nnt/myResume}{}
  {tuyendev96@gmail.com}
\end{tabular*}
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
    & \href{https://github.com/tuyen-nnt/myResume}{}
  {0932054596}
\end{tabular*}




%-----------EXPERIENCE-----------------
\section{Working Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {FPT Software}{Feb 2023 - Present}
      {Data Engineer - AVI - Data Capture}{}
      \resumeItemListStart
        \resumeItem{ETL transform}
          {Process transform aircraft data then share data between Airbus and Airlines.} 
        \resumeItem{Skywise Application Maintenance}
          {Follow requests to add feature or checking issue to fix applications. Deploy application for airlines.}
        \resumeItem{Resource Optimization}    
          {Research optimize data transformation to help reduce disk spillage, wide transformation and decrease build time by analyzing pipeline and applying appropriate techniques.}
      \resumeItemListEnd  
      
    \resumeSubheading
      {VNG Corp}{May 2019 - Nov 2022}
      {Data Engineer - Payment Data Platform}{Jul 2022 - Present}
      \resumeItemListStart
        \resumeItem{Data Collection}
        {Collect data from other functional teams, create processors on NiFi to consume new log.}
        \resumeItem{Implement API for data platform}
        {Implement \& deploy GRPC APIs for other teams in ZaloPay to get required data on K8s and physical environment.} 
        \resumeItem{Migration}
        {Migrate data between S3 and HDFS.}
      \resumeItemListEnd

      \resumeSubheadingNoTitle
      {Data Engineer - Prism Mobility}{Dec 2020 - Jun 2022}
      \resumeItemListStart
        \resumeItem{Data warehouse}
        {Add features, fix issues, create ETL pipeline transforming data to help product team make decisions and reports.}
        \resumeItem{Dashboard - Sale reporting system}
        {Maintain, fix issues and optimize data flows to provide data for customer efficiently.} 
        \resumeItem{Data visualization}
        {Visualize data using Excel and Tableau for any requests.}
        \resumeItem{Reconciliation and quality assurance}
        {Work with software engineers and partners to verify data.}
      \resumeItemListEnd
      %\\resumeItemListStart
      %\\resumeSubItemNormal
        %\{Data collection and visualization}
      %\\resumeSubItemNormal
        %\{Data Reconciliation}
      %\\resumeSubheadingNoTitle
      %\\resumeItemListEnd
      \resumeSubheadingNoTitle
      {Operations Executive - UniPass}{May 2019 - Dec 2020}
      
      \resumeItemListStart
        \resumeItem{Budget Controller}
          {Distribute and setup budget plan for incubator projects.} 
        \resumeItem{Facilities Controller}
          {Provide equipment and manage storage warehouse of incubator projects. Control import, export and purchase merchandises.}
        \resumeItem{Paperwork}
          {Edit and work with Legal team to proceed contracts and documents with external partners and government.}
      \resumeItemListEnd
      
    \resumeSubheading
      {Capgemini Vietnam}{Dec 2018 - May 2019}
      {Business Analyst - INDUS team}{}
      \resumeItemListStart
        \resumeItem{Documentation}
          {Turn requirements into documents for engineering team to maintain internal tools.} 
        \resumeItem{Administration}
            {Review tickets and grant permissions on internal resource for staffs in France and India.}
        \resumeItem{QC Support}    
            {Quality control for data migration from Teamforge to Sharepoint. }
      \resumeItemListEnd


    % \resumeSubheading
      % {Tourism Promotion Center - HCMC Department of Tourism}{Jan 2018 - Jul 2018}
      % {Collaborator}
      %\{Intern - Collaborator}{}
      %\resumeItemListStart
        %\resumeItem{Support visitors}
          %{Provide HCMC tourism information as well as introduce tourist destinations in Vietnam and response to all queries of tourists.}
        %\resumeItem{Administration}
          %{Manage and evaluate stock services and related infrastructure for visitor support sites in HCMC.}
      %\resumeItemListEnd

  
%-----------PROJECT ACHIEVEMENT-----------------
\section{Achievement \& Project}
  \resumeSubHeadingListStart 
    \resumeSubItem{\href{}{Award}}
      {Win 1st Prize of SheCodes Hackathon 2020. }
    \resumeSubItem{\href{https://github.com/tuyen-nnt/shortenLink}{ShortLink}}
      {A web-app to generate full link to a shorten link.}
    \resumeSubItem{BigO Green}
      {Elementary Algorithms Certificate}
\resumeSubHeadingListEnd


\section{Skills}
  \resumeSubHeadingListStart
    \resumeSubItem{Foreign Languages}
      {English, French.}
    \resumeSubItem{Languages}
      {Familiar with Python, SQL, HTML.}
      {Experience with Java, JavaScript, C/C++.}
    \resumeSubItem{Experience}
      {Spark, MySQL, Airflow, Jupyter, Kafka, HDFS, MongoDB, Amazon Web  Services, Tableau, basic Linux commands, basic Machine learning.}
\resumeSubHeadingListEnd

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Education, Ho Chi Minh city}{}
      {Bachelor in French language, Tourism}{2014 -- 2018}
    \resumeSubheading
      {Data Warehouse - The Ultimate Guide Udemy Certificate}{}
      {Master Data Warehousing, Dimensional Modeling and ETL Process}{2023}
    \resumeSubheading
      {Mastering Data Modeling Fundamentals}{2023}  
      {Entity - Relationship Techniques and Best practices}{2023}%{ETL and Data Pipelines with Shell, Airflow and Kafka; Big Data with Spark and Hadoop; etc.}{2022}
  \resumeSubHeadingListEnd


 %\section{Hobbies}
 % \resumeSubHeadingListStart
 %   \resumeSubItemNormal
 % \resumeSubHeadingListEnd


\section{Social activities}
  \resumeSubHeadingListStart
    \resumeSubItemNormal
      {Organizer of VietOpenInfra community to host events such as OpenInfra Days, Technical meetups, techtalks, etc.}
    \resumeSubItemNormal
      {Write Tech blogs. For further references see \url{http://tuyen-nnt.github.io}}
    \resumeSubItemNormal
      {Organize other tech events that attracts hundred of people such as Arduino Day, Mobile Fablab Vietnam, etc.}
\resumeSubHeadingListEnd


%\\section{References}
  %\\small{Will be provided upon requests}

%-------------------------------------------
\end{document}
